Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex
one more ref.

\begin{figure*}[t!]
\renewcommand{\arraystretch}{1.1}
  \begin{tabular}{cc}
    \begin{minipage}{.40\textwidth}
%        \small
      \renewcommand{\arraystretch}{1.1}{
        \begin{uprogram}
          \UNL{1} (\DEFINE\ (\abigfunction~\py)
          \UNL{2} $(Create\ a\ big\ closure\ and\ return)$ 
          \end{uprogram}}
        \renewcommand{\arraystretch}{1.1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\
(\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF\
$\psi_1\!\!:\,$ \px
            \UNL{4} \hspace*{.27cm} $\pi_3\!\!:\,
            $(\LET\ \pv\ $\leftarrow 0$ \IN
            \UNL{5} \hspace*{.32cm} $\pi_4\!\!:\,
(\SRETURN~\psi_2:\pv)$
            \UNL{4} \hspace*{.29cm}    $\pi_5\!\!:\, $(\LET~\pu\
$\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{.34cm}   $\pi_6\!\!:\, $(\LET~\py\
$\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{.34cm} $\pi_7\!\!:\,
            $(\LET~\pz\ $\leftarrow$ (1~+~\py) \IN
            \UNL{7} \hspace*{.34cm} $\pi_8\!\!:\,
(\SRETURN~\psi_3:\pz)$)))))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1.1}{
	  \begin{uprogram}
	  \UNL{1} $(\DEFINE\ (\main)$
           \UNL{2} \!\!$\pi_9\!\!:\, (\LET\  \pa\  \leftarrow
(\abigfunction\ \acdr)$ \IN
          \UNL{3} \!\!$\pi_{10}\!\!:\, (\LET\  \pb\  \leftarrow ($+$\ \pa\ \acdr)$
\IN
	  \UNL{4}   \hspace*{.05cm}$\pi_{11}\!\!:\,      $ (\LET\ \pc\
$\leftarrow  (\CONS\ \pb\ \NIL)$ \IN
          \UNL{5}   \hspace*{.15cm}    $\pi_{12}\!\!:\,
          $(\LET\ \pw\  $\leftarrow  (\length\ \pc)$ \IN
          \UNL{6}  \hspace*{.25cm}  $\pi_{13}\!\!:\,
(\SRETURN~\psi_4:\pw)))))$
\end{uprogram}}
        %%}
    \end{minipage}

@@

\section{Related Work} 
\label{sec:relatedwork}
Although augmenting  garbage collection with liveness  information has
been  studied earlier,  it was  mainly  in the  context of  imperative
languages~\cite{Albert,  Hirzel}.  Due  to   the  presence  of  global
variables  and mutation,  practical utility  of simple  liveness based
techniques are found to be inefficient.

>>>>

\begin{figure*}[t!]
\renewcommand{\arraystretch}{1.1}
  \begin{tabular}{cc}
    \begin{minipage}{.40\textwidth}
%        \small
        \renewcommand{\arraystretch}{1.1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\
(\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF\
$\psi_1\!\!:\,$ \px
            \UNL{4} \hspace*{.27cm} $\pi_3\!\!:\,
            $(\LET\ \pv\ $\leftarrow 0$ \IN
            \UNL{5} \hspace*{.32cm} $\pi_4\!\!:\,
(\SRETURN~\psi_2:\pv)$
            \UNL{4} \hspace*{.29cm}    $\pi_5\!\!:\, $(\LET~\pu\
$\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{.34cm}   $\pi_6\!\!:\, $(\LET~\py\
$\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{.34cm} $\pi_7\!\!:\,
            $(\LET~\pz\ $\leftarrow$ (1~+~\py) \IN
            \UNL{7} \hspace*{.34cm} $\pi_8\!\!:\,
(\SRETURN~\psi_3:\pz)$)))))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1.1}{
	  \begin{uprogram}
	  \UNL{1} $(\DEFINE\ (\main)$
           \UNL{2} \!\!$\pi_9\!\!:\, (\LET\  \pa\  \leftarrow$
           (
           \scalebox{0.8}{\psframebox[framearc=.5,
	fillcolor=lightgray,fillstyle=solid,framesep=2pt]{%
             \begin{tabular}{@{}c@{}}
               {a BIG closure}
             \end{tabular}}}
           ) \IN  
          \UNL{3} \!\!$\pi_{10}\!\!:\, (\LET\  \pb\  \leftarrow ($+$\ \pa\ \acdr)$
\IN
	  \UNL{4}   \hspace*{.05cm}$\pi_{11}\!\!:\,      $ (\LET\ \pc\
$\leftarrow  (\CONS\ \pb\ \NIL)$ \IN
          \UNL{5}   \hspace*{.15cm}    $\pi_{12}\!\!:\,
          $(\LET\ \pw\  $\leftarrow  (\length\ \pc)$ \IN
          \UNL{6}  \hspace*{.25cm}  $\pi_{13}\!\!:\,
(\SRETURN~\psi_4:\pw)))))$
\end{uprogram}}
        %%}
    \end{minipage}

@@

\section{Related Work} 
\label{sec:relatedwork}
Although augmenting  garbage collection with liveness  information has
been  studied earlier,  it was  mainly  in the  context of  imperative
languages~\cite{Albert, Hirzel,  khedker07heap}.  Due to  the presence
of global variables and mutation, practical utility of simple liveness
based techniques are found to be inefficient.
